Handling String-Number Conversion in String Constraint Solving

### 2019-11-15 draft.tex
add an alternative way to describe correctness lemmas

The following lemma states the correctness of this construction, and it follows from Corollary~\ref{corollary:pfa}, Lemma~\ref{lemma:synccorrect}. 
Intuitively, it says that the resulting constraint represents precisely the restriction of $L(A)$ to the domain $\semof{A_x}$, the $A_x$-encodings of the strings in $L(A)\cap\semof{A_x}$. 
%

%
\begin{lemma}\label{lemma:memcorrect}
	${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
\end{lemma}

@@

@@

\end{lemma}
\yfc{sorry still ugly, the shifting of epsilon makes it a mess here}

\hide{
\begin{lemma}\label{lemma:sticorrect_pos}
	$\semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}} = \{(I\cup\pim \cup I_n) \mid  I_n(n)= \sti{\decode {A_x}(I\cup\pim)}\} $. 
\end{lemma}
In this case, $x$ encodes a number. The lemma says when the models we add to $\Phi_O$ represents a word in $\semof{A_x}$ whose integer value is exactly the model for $n$.

>>>>

The following lemma states the correctness of this construction, and it follows from Corollary~\ref{corollary:pfa}, Lemma~\ref{lemma:synccorrect}. 
Intuitively, it says that the resulting constraint represents precisely the restriction of $L(A)$ to the domain $\semof{A_x}$, the $A_x$-encodings of the strings in $L(A)\cap\semof{A_x}$. 
%
\begin{lemma}\label{lemma:memcorrect}  ${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
\end{lemma}
%
(An alternative description)
\begin{lemma}\label{lemma:memcorrect} For all $w\in \semof{A_x}$, %$(I\cup\pim)$ in ${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}}$ such that $w =\decode {A_x}(I\cup\pim)$ if and only if $w \in L(A)$.
%	$$\exists (I\cup\pim) \in {\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}}. w =\decode {A_x}(I\cup\pim)$$
	\begin{center}
	$\exists (I\cup\pim)$ in ${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}}$ s.t. $w =\decode {A_x}(I\cup\pim)$\\
		iff\\
		$w \in L(A)$.
	\end{center}
%	${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
\end{lemma}

@@

(An alternative description)

\begin{lemma}\label{lemma:eqcorrect} For all $w_1 \in \semof{A_{x_1}} \ldots w_m \in \semof{A_{x_m}}$, we have

	\begin{center}
		$\exists (I^1\cup\pim^1)\cup\ldots\cup (I^m\cup\pim^m)$ in $\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} }$ s.t. $w_1=\decode A_{x_1}(I^1\cup\pim^1),\ldots,w_m=\decode A_{x_m}(I^m\cup\pim^m)$\\
		iff\\
		$w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m$ and\\
		$\forall i,j \in [1,m]: x_i=x_j \Longrightarrow w_i=w_j$.
	\end{center}
\end{lemma}

@@

\end{lemma}
\yfc{sorry still ugly, the shifting of epsilon makes it a mess here}
(An alternative description)
\begin{lemma}\label{lemma:sticorrect}
	For all $w \in \semof{A_{x}}$ and $c \in \mathbb{Z}$, we have 
	\begin{center}
		$\exists (I\cup\pim \cup I_n)  \in \semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}}$ s.t. $w=\decode {A_x}(I\cup\pim)$ and $I_n(n)=c$\\
		iff\\
		$c= \sti{w}$.
	\end{center}

\end{lemma}
\hide{
\begin{lemma}\label{lemma:sticorrect_pos}
	$\semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}} = \{(I\cup\pim \cup I_n) \mid  I_n(n)= \sti{\decode {A_x}(I\cup\pim)}\} $. 
\end{lemma}
In this case, $x$ encodes a number. The lemma says when the models we add to $\Phi_O$ represents a word in $\semof{A_x}$ whose integer value is exactly the model for $n$.
